Details of specific functions

### 2025-04-29 inst/gitbook/03_specific-tutorials.Rmd
minor fixes

The `displacements` distance is the ratio between the `centroids` distance and the `centroids` distance with `centroid = 0`.
Note that it is possible to measure a ratio from another point than `0` using the `reference` argument.
It gives indication of the relative displacement of elements in the multidimensional space: a score  >1 signifies a displacement *away* from the reference. A score of >1 signifies a displacement *towards* the reference.

>>>>

The `displacements` distance is the ratio between the `centroids` distance and the `centroids` distance with `centroid = 0`.
Note that it is possible to measure a ratio from another point than `0` using the `reference` argument.
It gives indication of the relative displacement of elements in the multidimensional space: a score > 1 signifies a displacement away from the reference. A score of < 1 signifies a displacement *towards* the reference.
